\documentclass{article}
\usepackage{hyperref}

\begin{document}

\title{List of Popular Datasets Sites}
\author{}
\date{}
\maketitle

\section{Deep Learning / Machine Learning Datasets Sites}
\begin{enumerate}
    \item \textbf{UCI Machine Learning Repository}: A popular resource for datasets in the machine learning community.
    \begin{itemize}
        \item \url{https://archive.ics.uci.edu/ml/index.php}
    \end{itemize}

    \item \textbf{Google Dataset Search}: A tool by Google that helps you find datasets stored across the web.
    \begin{itemize}
        \item \url{https://datasetsearch.research.google.com/}
    \end{itemize}

    \item \textbf{AWS Public Datasets}: A collection of publicly available datasets hosted by Amazon Web Services.
    \begin{itemize}
        \item \url{https://registry.opendata.aws/}
    \end{itemize}

    \item \textbf{Microsoft Azure Open Datasets}: A repository of open datasets curated by Microsoft.
    \begin{itemize}
        \item \url{https://azure.microsoft.com/en-us/services/open-datasets/}
    \end{itemize}

    \item \textbf{OpenML}: An online platform for sharing and finding datasets, algorithms, and experiments.
    \begin{itemize}
        \item \url{https://www.openml.org/}
    \end{itemize}

    \item \textbf{Data.gov}: The U.S. government's open data site, which includes datasets on various topics.
    \begin{itemize}
        \item \url{https://www.data.gov/}
    \end{itemize}

    \item \textbf{Quandl}: A platform for financial, economic, and alternative datasets.
    \begin{itemize}
        \item \url{https://www.quandl.com/}
    \end{itemize}

    \item \textbf{Kaggle Datasets}: Although you mentioned not to use Kaggle, it's worth noting for completeness.
    \begin{itemize}
        \item \url{https://www.kaggle.com/datasets}
    \end{itemize}

    \item \textbf{Google Cloud Public Datasets}: A collection of public datasets hosted by Google Cloud.
    \begin{itemize}
        \item \url{https://cloud.google.com/public-datasets}
    \end{itemize}

    \item \textbf{Papers with Code}: A site that links research papers with their associated datasets and code.
    \begin{itemize}
        \item \url{https://paperswithcode.com/datasets}
    \end{itemize}

    \item \textbf{Machine Learning Datasets at Awesome Public Datasets}: A curated list of public datasets on GitHub.
    \begin{itemize}
        \item \url{https://github.com/awesomedata/awesome-public-datasets#machine-learning}
    \end{itemize}

    \item \textbf{Stanford Large Network Dataset Collection (SNAP)}: Datasets for social network analysis and more.
    \begin{itemize}
        \item \url{https://snap.stanford.edu/data/}
    \end{itemize}

    \item \textbf{KDNuggets Datasets}: A collection of datasets recommended by KDNuggets for machine learning projects.
    \begin{itemize}
        \item \url{https://www.kdnuggets.com/datasets/index.html}
    \end{itemize}

    \item \textbf{AI2 Datasets by Allen Institute for AI}: A collection of datasets provided by the Allen Institute for AI.
    \begin{itemize}
        \item \url{https://allenai.org/data}
    \end{itemize}
\end{enumerate}


\section{Some IoT / Cyber Physical Systems Datasets for Machine Learning and Deep Learning}

\begin{enumerate}
    \item \textbf{UCI Machine Learning Repository - Smart Home Dataset}: Contains data from a real smart home setup including various sensors and environmental readings.
    \begin{itemize}
        \item \url{https://archive.ics.uci.edu/ml/datasets/Smart+Home+Dataset+with+Weather+Information}
    \end{itemize}

    \item \textbf{Intel Berkeley Research Lab - Sensor Data}: Sensor data from a deployment of 54 sensors in the Intel Berkeley Research lab.
    \begin{itemize}
        \item \url{http://db.lcs.mit.edu/labdata/labdata.html}
    \end{itemize}

    \item \textbf{Smart Data Set}: Data from various IoT devices deployed in real homes.
    \begin{itemize}
        \item \url{http://traces.cs.umass.edu/index.php/Smart/Smart}
    \end{itemize}

    \item \textbf{IoT Network Intrusion Dataset (TON\_IoT)}: A dataset for cybersecurity applications in IoT.
    \begin{itemize}
        \item \url{https://research.unsw.edu.au/projects/toniot-datasets}
    \end{itemize}

    \item \textbf{CASAS Smart Home Project}: Datasets from the CASAS smart home project, which includes sensor data for activity recognition.
    \begin{itemize}
        \item \url{http://casas.wsu.edu/datasets/}
    \end{itemize}

    \item \textbf{CityPulse: Smart City Datasets}: A collection of datasets for various smart city applications, including transportation and environmental monitoring.
    \begin{itemize}
        \item \url{http://iot.ee.surrey.ac.uk:8080/datasets.html}
    \end{itemize}

    \item \textbf{Pecan Street Dataport}: Smart grid data including residential energy consumption and solar power generation.
    \begin{itemize}
        \item \url{https://dataport.pecanstreet.org/}
    \end{itemize}

    \item \textbf{Tennessee Eastman Process Simulation Data}: A dataset used for monitoring and fault diagnosis in industrial processes.
    \begin{itemize}
        \item \url{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/6C3JR1}
    \end{itemize}

    \item \textbf{GreenButton Energy Data}: Standardized format for representing energy usage information.
    \begin{itemize}
        \item \url{https://www.greenbuttondata.org/}
    \end{itemize}

    \item \textbf{Ocean Observatories Initiative (OOI) Data}: Oceanographic data collected from various sensors deployed in the ocean.
    \begin{itemize}
        \item \url{https://ooinet.oceanobservatories.org/}
    \end{itemize}

    \item \textbf{Air Quality Data Set}: Real-time data on air quality parameters collected from various sensors.
    \begin{itemize}
        \item \url{https://archive.ics.uci.edu/ml/datasets/Air+Quality}
    \end{itemize}

    \item \textbf{UK-DALE: UK Domestic Appliance-Level Electricity Dataset}: A dataset for understanding energy consumption patterns in households.
    \begin{itemize}
        \item \url{https://data.ukedc.rl.ac.uk/browse/edc/efficiency/residential/Electricity-Use}
    \end{itemize}

    \item \textbf{IEEE DataPort: Datasets for IoT and Cyber-Physical Systems}: A collection of datasets for various IoT and CPS applications.
    \begin{itemize}
        \item \url{https://ieee-dataport.org/}
    \end{itemize}

    \item \textbf{OpenSky Network - Air Traffic Data}: Air traffic surveillance data for monitoring and analysis.
    \begin{itemize}
        \item \url{https://opensky-network.org/datasets}
    \end{itemize}

    \item \textbf{SECOM Manufacturing Data}: Dataset used for anomaly detection in semiconductor manufacturing.
    \begin{itemize}
        \item \url{https://archive.ics.uci.edu/ml/datasets/SECOM}
    \end{itemize}

    \item \textbf{NASA Prognostics Data Repository}: Datasets for the study of prognostics and health management.
    \begin{itemize}
        \item \url{https://www.nasa.gov/content/prognostics-center-of-excellence-data-set-repository}
    \end{itemize}

    \item \textbf{Smart Cities Open Data Portal}: A portal offering various datasets related to smart cities applications.
    \begin{itemize}
        \item \url{https://data.smartcity.barcelona/}
    \end{itemize}

    \item \textbf{Aranet4: Environmental Sensor Data}: Real-time environmental data including temperature, humidity, and CO2 levels.
    \begin{itemize}
        \item \url{https://aranet.com/en/download-category/environmental-data/}
    \end{itemize}

    \item \textbf{MeteoNet: Weather Prediction Data}: A dataset for weather prediction using IoT sensor data.
    \begin{itemize}
        \item \url{https://meteonet.umr-cnrm.fr/dataset.html}
    \end{itemize}

    \item \textbf{OpenAIRE: Research Data for IoT and CPS}: A repository of open access research data for IoT and CPS applications.
    \begin{itemize}
        \item \url{https://www.openaire.eu/}
    \end{itemize}
\end{enumerate}

\end{document}
